---
title: "Who does more pushups"
author: "Ebony Ervin"
date: "October 7 2017"
output: html_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

Several years ago some MAT 111 students who were on the footbal team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

```{r eval=FALSE}
data(pushups)
View(pushups)
help(pushups)
```

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of runninga and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?


# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Depending on the type of information I see in my data will determine which plot will be more useful to analyze the information i need. I have categorical data called position and numerical data called pushups. I plan to the use a box plot to display the data. Im going to use favcstats as a numerical method to see if they are different. Finally Im going to use a Ttest to make  inferential sense of this data.




# Results
<!--You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.!-->

Based on the numerical plot i see that the median for line players was 14.5 whereas the median for skill players were 57.50. In addition I noticed in the box plot that the numbers were realatively the same. This leads me to believe that skills players do more pushups than line players.


 In the numerical graph I coulsd see that the 
## Graphical Results
<!--Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.!-->
Below is the box plot of pushups and positions.
```{r}
bwplot(pushups~position,data=pushups,
       main="pushups by position",
       xlab="position",
       ylab="pushups")
```
  
Looking at the box plot you will see that the box on the left is below the box on the right. This indicates that skillplayers seem to do a lot more pushups than line players.

## Numerical Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
favstats(pushups~position,data=pushups)
```
Based on the numerical summary you will see that line players only did 17 pushups as opposed to 49 pushups done by skill players. It seems that skill players tripled the amount of pushups done by line players.  

# Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

tttestGC(pushups~positions,data=pushups)
```{r}
t.test(pushups~position,data = pushups)
```

Based on the information I have gathered after conducting the ttest I can see that the mean for the skills players is 49.72727 and the mean for the line players is 17.12500 in addition I see that the p- value is 000000.9421 which  is a really small number. This indicates that I should reject the null hypothisis, due to the fact that the means of the two data sets are not equal.



# Discussion and Conclusion
<!--State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.!-->

Based on all the information gathered during the course of this project it is safe for one to assume that skills players do more pushups than line players.



